\textbf{Code exploration}

### 2024-10-28 paper_code.Rnw
Update paper_code.Rnw

@@

par(mfrow=c(1,2))

>>>>

\subsection{Reproduce Figure 1}
<<Figure 1, echo=FALSE, results=hide>>=
# a sequence of true HR.
t.d <- seq(0, 1, 0.01)

n <- 309
sd <- sqrt((2*2^2)/n) #sigma assumed to be 2?
cut.ssig <- 0.8 # statistical significance NV=1
cut.crel <- 0.8 # critical relevance
pp.go <- pnorm(cut.crel, t.d, sd)
pp.ngo <- 1- pnorm(cut.ssig, t.d, sd)
pp.intd <- 1 -pp.go - pp.ngo

n <- 420
sd <- sqrt((2*2^2)/n) #sigma assumed to be 2?
cut.ssig <- 0.83 # statistical significance NV=1
cut.crel <- 0.8 # critical relevance
pp.go6 <- pnorm(cut.crel, t.d, sd)
pp.ngo6 <- 1- pnorm(cut.ssig, t.d, sd)
pp.intd6 <- 1 -pp.go6 - pp.ngo6

png("Figure 1.png", width = 1200, height = 800, res = 150)
par(mfrow=c(1,2))
plot(t.d, pp.go, type="l", xlab= "Hazard Ratio", ylab="Probability", main="n=309", col="green", ylim=c(0,1),xlim=c(0.3,1))
lines(t.d, pp.ngo, type="l", col="red")
lines(t.d, pp.intd, type="l", col="darkgoldenrod1")
abline(v=0.8, lty=1)

plot(t.d, pp.go6, type="l", xlab= "Hazard Ratio", ylab="Probability", main="n=420", col="green", ylim=c(0,1),xlim=c(0.3,1))
lines(t.d, pp.ngo6, type="l", col="red")
lines(t.d, pp.intd6, type="l", col="darkgoldenrod1")
abline(v=0.8, lty=1)
dev.off()

@
\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{Figure 1.png}
\caption{Reproduce Figure 1}
\end{figure}

@@
